### 2024-03-13 HickernellFredSpecialSession.tex
Updates from Overleaf

Low discrepancy (LD) sequences, such as lattice, digital, and Halton sequences, can be used to estimate multivariate integrals with greater computational efficiency than independent and identically distributed (IID) sequences.  The use of LD sequences for density estimation has been less studied in the past, but studied recently %\cite{AbdEtal21a,LEcuyer2022b,LEcPuc20a} 
[1--3].

>>>>

Low discrepancy (LD) sequences, such as lattice, digital, and Halton sequences, are well known to estimate multivariate integrals with greater computational efficiency than independent and identically distributed (IID) sequences.  The use of LD sequences for density estimation has been studied recently %\cite{AbdEtal21a,LEcuyer2022b,LEcPuc20a} 
[1--3].
